\documentclass[12pt]{article}

\usepackage[margin=0.4in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mathptmx}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{fontawesome5}

% Hyperlink styling — ATS-safe, no colored boxes
\hypersetup{colorlinks=true, linkcolor=black, urlcolor=black}

% Remove page numbers
\pagestyle{empty}

% Custom commands
\newcommand{\name}[1]{{\fontsize{20pt}{20pt}\selectfont\textbf{#1}}}
\newcommand{\sectionhead}[1]{{\fontsize{12pt}{14pt}\selectfont\textbf{#1}}\vspace{2pt}\hrule\vspace{3pt}}

% Tight spacing for one-page format
\setlist[itemize]{itemsep=0pt, topsep=1pt, leftmargin=16pt}
\parskip=1pt

\begin{document}

% ==================== HEADER ====================
\begin{center}
    \name{Jeeva G}
    \vspace{2pt}

    {\fontsize{10.5pt}{10.5pt}\selectfont Full-Stack Developer}

    \vspace{2pt}

    \href{mailto:priyagovinth2019@gmail.com}{priyagovinth2019@gmail.com} \quad
    +91 6369235064 \quad
    \href{https://linkedin.com/in/jeevain/}{linkedin.com/in/jeevain} \quad
    \href{https://github.com/jeeva2470041}{github.com/jeeva2470041}
\end{center}

\vspace{3pt}

% ==================== 1. OBJECTIVE ====================
\sectionhead{Objective}

Second-year M.Tech (Integrated) Computer Science student at SSN College of Engineering (CGPA: 8.01) with a strong focus on solving real-world problems through practical, scalable solutions. Adaptable and quick to learn new technologies, with proven ability to perform in fast-paced, deadline-driven environments. Currently advancing skills in machine learning and system design while seeking internship opportunities to contribute effectively from the outset.

\vspace{4pt}

% ==================== 2. EDUCATION ====================
\sectionhead{Education}

\textbf{M.Tech(Integrated) -- Computer Science and Engineering} \hfill

SSN College of Engineering, Chennai -- CGPA: 8.01 (2024--2029) (Pursuing)

\textbf{HSC -- 12th Grade} \hfill

Adithya Vivekananda Hr. Sec School, Villupuram -- 94.87\% (2023--2024)

\vspace{4pt}

% ==================== 3. SKILLS ====================
\sectionhead{Skills}

\begin{tabular}{ l l }
\textbf{Languages:} & Java, Python, C, JavaScript, SQL, Dart \\
\textbf{Frontend:} & React.js, HTML, CSS, Flutter \\
\textbf{Backend:} & Node.js, Firebase \\
\textbf{Databases:} & MongoDB, MySQL, Neo4j \\
\textbf{AI / ML:} & TensorFlow, CLIP, FAISS \\
\textbf{Tools:} & Git, GitHub, GitLab \\
\end{tabular}

\vspace{4pt}

% ==================== 4. PROJECTS ====================
\sectionhead{Projects}

\textbf{PayTrace - Payment Tracker}
\begin{itemize}
    \item Developed an automated UPI expense tracker that parses SMS and push notifications from 5+ payment apps (Google Pay, PhonePe, Paytm) to eliminate manual data entry.
    \item Implemented ML-based transaction categorization achieving 92\%+ accuracy, with interactive spending visualizations that reduced user expense-tracking effort by approximately 80\%.
\end{itemize}

\vspace{2pt}
\textbf{NewsImages Retrieval and Generation}
\begin{itemize}
    \item Built a dual-pipeline image recommendation system processing 8,500+ news articles using CLIP embeddings and FAISS vector search for sub-second semantic retrieval.
    \item Engineered a fallback pipeline using Stable Diffusion XL to generate editorial-quality synthetic images when no relevant match exists, meeting full MediaEval 2025 submission guidelines.
\end{itemize}

\vspace{2pt}
\textbf{EcoFeed - Food Donation Platform}
\begin{itemize}
    \item Architected a full-stack food waste reduction platform with location-based matching algorithm connecting surplus food donors to 50+ nearby NGOs and orphanages.
    \item Implemented real-time WebSocket notifications and an impact tracking dashboard measuring meals redistributed and waste prevented.
\end{itemize}

\vspace{4pt}

% ==================== 5. HACKATHONS & ACHIEVEMENTS ====================
\sectionhead{Hackathons \& Achievements}

\begin{itemize}
    \item \textbf{Winner} -- St. Joseph College Hackathon (2025): Developed PayTrace, selected as best project among 50+ teams.
    \item \textbf{Participant} -- SIH NATPAC (2025): Built a consent-based travel data collection app for NATPAC organisation.
    \item \textbf{Participant} -- Google TechSprint (2025): Developed Campus share platform.
\end{itemize}

\vspace{4pt}

% ==================== 6. CERTIFICATIONS ====================
\sectionhead{Certifications}

\textbf{NPTEL} -- Privacy and Security in Online Social Media $|$ \textbf{Google TechSprint} -- Participation Certificate

\end{document}
