\documentclass[11pt]{article}

\usepackage[margin=0.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{ragged2e}

% Color definitions
\definecolor{darkblue}{RGB}{0, 102, 204}
\definecolor{lightgray}{RGB}{240, 240, 240}

% Remove page numbers and default header/footer
\pagestyle{empty}

% Custom commands
\newcommand{\name}[1]{{\fontsize{24pt}{24pt}\selectfont\textbf{#1}}}
\newcommand{\sectionhead}[1]{{\color{darkblue}\fontsize{12pt}{12pt}\selectfont\textbf{#1}}\vspace{4pt}\hrule\vspace{6pt}}
\newcommand{\subsectionhead}[2]{{\textbf{#1}} \hfill {\textit{#2}}\vspace{2pt}}
\newcommand{\subsubsectionhead}[2]{{\textbf{#1}} $|$ {\textit{#2}}\vspace{2pt}}

% Reduce spacing
\setlist[itemize]{itemsep=2pt, topsep=0pt, leftmargin=20pt}

\begin{document}

% ==================== HEADER ====================
\begin{center}
    \name{Arivuchezhiyan E}
    \vspace{3pt}
    
    Chennai, India $|$ \href{mailto:arivuchezhiyan000@gmail.com}{\faEnvelope \, arivuchezhiyan000@gmail.com} $|$ \faPhone \, +91 7010818264 $|$ 
    \href{https://linkedin.com/in/arivuchezhiyan}{\faLinkedin \, linkedin.com/in/arivuchezhiyan} $|$ 
    \href{https://github.com/arivuchezhiyan}{\faGithub \, github.com/arivuchezhiyan}
\end{center}

\vspace{6pt}

% ==================== EXECUTIVE SUMMARY ====================
\sectionhead{EXECUTIVE SUMMARY}

First-year M.Tech Integrated CSE student at SSN with hands-on experience building software across systems programming, full-stack web development, and cross-platform mobile engineering. Built and shipped projects spanning a custom OS kernel in C/x86 Assembly, a real-time MERN ride-hailing platform, and an encrypted 12-feature Windows–Android integration suite. Ranked 2nd in XII State Board examinations (571/600) and currently maintaining a 7.656 CGPA.

\vspace{6pt}

% ==================== EDUCATION ====================
\sectionhead{EDUCATION}

\subsectionhead{M.Tech (Int) CSE — Sri Sivasubramaniya Nadar College (SSN)}{2024 – 2029}
CGPA: 7.656

\subsectionhead{XII (State) — Paarivallal Higher Secondary School, Ariyalur}{2023}
Marks: 571/600 (Rank 2)

\subsectionhead{X (State) — Paarivallal Higher Secondary School, Ariyalur}{2021}

\vspace{6pt}

% ==================== PROJECTS ====================
\sectionhead{PROJECTS}

\subsectionhead{Assistant}{Python, AI, Automation \hfill 2025}
\begin{itemize}
    \item Built a modular AI assistant in Python integrating speech recognition, task scheduling, and OS-level automation across 5+ independently deployable plugins.
    \item Reduced manual task execution time by approximately 60\% through natural language command routing and cross-application automation pipelines.
\end{itemize}

\subsectionhead{OpenContinuity}{Electron, TypeScript, Kotlin, AES-256-GCM \hfill 2025}
\begin{itemize}
    \item Designed a 12-feature Windows–Android integration suite (clipboard sync, file transfer, screen mirroring, notifications, battery monitoring) using Electron and Kotlin with sub-50ms local network latency.
    \item Secured all inter-device communication with AES-256-GCM encryption and ECDH key exchange, and automated device discovery via mDNS, eliminating manual IP configuration.
\end{itemize}

\subsectionhead{Uber Clone}{MERN Stack, React, Socket.io, Stripe API \hfill 2025}
\begin{itemize}
    \item Built a full-stack MERN ride-hailing platform with real-time GPS tracking (Socket.io + Leaflet.js) and role-based dashboards for 3 user types: customers, drivers, and admins.
    \item Integrated Stripe payment workflows supporting end-to-end transaction processing, ride history, and user rating persistence on MongoDB Atlas.
\end{itemize}

\subsectionhead{Elite OS}{C, x86 Assembly, Kernel Development \hfill 2024}
\begin{itemize}
    \item Developed a custom xv6-derived OS kernel in C and x86 Assembly, implementing preemptive process scheduling, virtual memory paging, and 8 custom system calls.
    \item Achieved full usertests.c suite pass rate, validating memory allocator correctness, context-switch integrity, and system call isolation under concurrent load.
\end{itemize}

\vspace{6pt}

% ==================== TECHNICAL SKILLS ====================
\sectionhead{TECHNICAL SKILLS}

\textbf{Languages:} C, C++, Python (Scripting, Automation), Java, JavaScript, Assembly (x86)

\textbf{Frontend:} React.js, HTML, CSS, JavaScript

\textbf{Mobile:} Flutter, Kotlin

\textbf{Backend:} Node.js, Express.js, Firebase

\textbf{Databases:} MongoDB, SQL

\textbf{Tools \& Platforms:} Git, GitHub, Socket.io, Electron

\textbf{CS Fundamentals:} Data Structures \& Algorithms, OS Internals, Systems Design

\vspace{6pt}

% ==================== CERTIFICATIONS & COURSES ====================
\sectionhead{CERTIFICATIONS \& COURSES}

Google — \textbf{Privacy and Security Fundamentals:} Certificate \quad $|$ \quad NPTEL — \textbf{Affective Computing} (In Progress)

Embedded Development Workshop — \textbf{Hardware Systems:} Certificate

\vspace{6pt}

% ==================== CLUBS AND ACTIVITIES ====================
\sectionhead{CLUBS AND ACTIVITIES}

SSN Coding Club (UI/UX Domain Member) $|$ IEEE Computer Society SSN (Volunteer) \hfill 2025 – Present

NSO Volunteer (Inter-college Sports Coordinator) $|$ Hackathons (Participated at SNU \& St. Joseph's)

\end{document}
